Virtual Memory Assisted Transactional Memory for Dynamic Languages

### 2014-06-02 talk/dls2014/paper/paper.tex
comment some currently unused references

\begin{figure}[h]
  \centering
  \includegraphics[width=1\columnwidth]{plots/performance_nojit.pdf}
  \caption{Comparing runtime between interpreters without a JIT\label{fig:performance-nojit}}
\end{figure}

@@

\begin{figure}[h]
  \centering
  \includegraphics[width=1\columnwidth]{plots/performance.pdf}
  \caption{Comparing runtime between interpreters with JIT\label{fig:performance-jit}}
\end{figure}

@@

\bibitem{dan07}
  Dan Grossman. 2007. The transactional memory / garbage collection
  analogy. \emph{In Proceedings of the 22nd annual ACM SIGPLAN
    conference on Object-oriented programming systems and
    applications} (OOPSLA '07).

@@

\bibitem{felber07}
  Felber, Pascal, et al. "Transactifying applications using an open
  compiler framework." \emph{TRANSACT}, August (2007): 4-6.

\bibitem{bill06}
  Bill McCloskey, Feng Zhou, David Gay, and Eric
  Brewer. 2006. Autolocker: synchronization inference for atomic
  sections. \emph{In Conference record of the 33rd ACM SIGPLAN-SIGACT
  symposium on Principles of programming languages (POPL '06)}. ACM,
  New York, NY, USA

@@

\bibitem{leis14}
  Leis, Viktor, Alfons Kemper, and Thomas Neumann. "Exploiting
  Hardware Transactional Memory in Main-Memory Databases."
  \emph{Proc. of ICDE}. 2014.

\bibitem{biased}
  Kenneth Russell and David Detlefs. 2006. Eliminating
  synchronization-related atomic operations with biased locking and
  bulk rebiasing. \emph{In Proceedings of the 21st annual ACM SIGPLAN
    conference on Object-oriented programing, systems, languages, and
    applications} (OOPSLA '06).

>>>>

\begin{figure}[h]
  \centering
  \includegraphics[width=1\columnwidth]{plots/performance_nojit.pdf}
  \caption{Comparing execution time between interpreters without a JIT\label{fig:performance-nojit}}
\end{figure}

@@

\begin{figure}[h]
  \centering
  \includegraphics[width=1\columnwidth]{plots/performance.pdf}
  \caption{Comparing execution time between interpreters with JIT\label{fig:performance-jit}}
\end{figure}

@@

% \bibitem{dan07}
%   Dan Grossman. 2007. The transactional memory / garbage collection
%   analogy. \emph{In Proceedings of the 22nd annual ACM SIGPLAN
%     conference on Object-oriented programming systems and
%     applications} (OOPSLA '07).

@@

% \bibitem{felber07}
%   Felber, Pascal, et al. "Transactifying applications using an open
%   compiler framework." \emph{TRANSACT}, August (2007): 4-6.

% \bibitem{bill06}
%   Bill McCloskey, Feng Zhou, David Gay, and Eric
%   Brewer. 2006. Autolocker: synchronization inference for atomic
%   sections. \emph{In Conference record of the 33rd ACM SIGPLAN-SIGACT
%   symposium on Principles of programming languages (POPL '06)}. ACM,
%   New York, NY, USA

@@

% \bibitem{leis14}
%   Leis, Viktor, Alfons Kemper, and Thomas Neumann. "Exploiting
%   Hardware Transactional Memory in Main-Memory Databases."
%   \emph{Proc. of ICDE}. 2014.

% \bibitem{biased}
%   Kenneth Russell and David Detlefs. 2006. Eliminating
%   synchronization-related atomic operations with biased locking and
%   bulk rebiasing. \emph{In Proceedings of the 21st annual ACM SIGPLAN
%     conference on Object-oriented programing, systems, languages, and
%     applications} (OOPSLA '06).
